\documentclass{resume}

\name{Jahziah Wagner}

\ifshowfooter
  \address{ Phone +46 (0)760-335 220 \\ Email jahziah@bytelope.com }
  \address{ \textbf{Bytelope AB} \\ Bennebolsgatan 14 \\ 163 50 Spånga, Stockholm }
\fi

\begin{document}

% Professional Summary
  \noindent
  \linebreak
  Experienced Software Developer with a strong foundation in Java EE, Spring Boot, and Microservices. Adept at agile methodologies and experienced in streamlining development processes. Committed to developing practical, user-centric solutions that align with organizational objectives.

  \begin{rSection}{Experience}
    \begin{rSubsection}{KINDRED PEOPLE AB}{August 2021 -- Present}{Pay and Withdraw Experience - Software Engineer Java}{Stockholm}
      \bItem Skillfully developed and maintained integrations with numerous payment service providers including \textit{Adyen, Brite, Earthport, Nuvei, Swish, Trustly, and Worldpay}.
      \bItem Developed a deep understanding of KYC processes and the payments industry, improving my knowledge of customer verification and compliance.
      \bItem Successfully enabled seamless deposits and withdrawals across Kindred Group's various brands, such as \textit{Unibet, Maria Casino, and Ottokasino}, enhancing customer payment experiences and operational efficiency.
      \bItem Served as Incident Manager, efficiently addressing operational incidents to ensure rapid service restoration and business continuity.
      \techItem Frontend in \textbf{React}. Backend with \textbf{Java 17} and \textbf{Spring Boot 3}. Real-time messaging using \textbf{Solace PubSub+ Event Broker}. Database management with \textbf{Oracle}. Container orchestration with \textbf{Kubernetes} \& \textbf{Docker}. Identity and access mana
      gement with \textbf{Okta}. Build and dependency management with \textbf{Maven}. CI/CD with \textbf{Jenkins}. Log analysis \& monitoring using \textbf{Splunk} \& \textbf{Grafana}. Version control with \textbf{Git}. Running on \textbf{Linux/Unix}. Project management following \textbf{Scrum} and \textbf{Kanban} methodologies.
    \end{rSubsection}

    \begin{rSubsection}{SVENSK TRAVSPORT AB}{June 2020 -- March 2021}{Backend - Development Lead}{Stockholm}
      \bItem Led backend API development for horse racing at svenskgalopp.se, guiding a team with agile methodologies for efficient project progression. Managed the transition from outsourced to in-house development, enhancing control and quality. Fostered a democratic decision-making environment, ensuring active team participation.
      \bItem Streamlined the management of approximately 100 microservice repositories, significantly improving operational efficiency. Optimized engagement with overseas consultants to enhance productivity and outcomes. Successfully delivered the new gallop web API, contributing substantially to the project’s success.
      \techItem Backend in \textbf{Java 11} with \textbf{Spring Boot}, database management with \textbf{Oracle Database}, container orchestration with \textbf{Kubernetes} and \textbf{Docker}, cloud services on \textbf{Google Cloud Platform}, development on \textbf{Linux/Unix}, monitoring with \textbf{Grafana}, dependency management with \textbf{Maven}, version control with \textbf{Git}. Project management following \textbf{Scrum} methodology.
    \end{rSubsection}

    \begin{rSubsection}{ERICSSON AB}{March 2019 -- January 2020}{Guided Sales Digital Platform - Software Developer}{Stockholm}
      \bItem Played a key role in the development of the ``Guided Sales Digital Platform (GSDP)'' for LTE \& 5G within a mid-sized team, employing agile methodologies.
      \bItem This tool significantly enhanced the sales configuration process.
      \bItem Received extensive training in RAN, baseband, radio, antenna, and carrier theory, and developed a deep understanding of the Ericsson hardware portfolio for LTE \& 5G solutions.
      \techItem Frontend in \textbf{Vue.js 2}. Backend with \textbf{Java 11} and \textbf{Spring Boot 2}. Database management with \textbf{CosmosDB}, \textbf{Neo4j}, and \textbf{PostgreSQL}. Integration with \textbf{SAP Hybris}. Infrastructure management with \textbf{Docker} and cloud services on \textbf{Azure}. Identity and access control using \textbf{OAuth2}. Version control with \textbf{Git}. Running on \textbf{Unix}.
    \end{rSubsection}

    \pagebreak

    \begin{rSubsection}{INERA AB}{May 2018 -- February 2019}{Hjälpmedelstjänsten 2.0 - Software Developer}{Stockholm}
      \bItem Successfully led the data migration process crucial for the launch of Hjälpmedelstjänsten 2.0. Managed the intricate task of extracting and harmonizing large volumes of diverse data, received intermittently from various administrative regions and their partners.
      \bItem Provided vital decision-making support to operations managers through comprehensive data analysis.
      \bItem Proactively identified and addressed potential issues, offering data-driven solutions to enhance operational efficiency.
      \bItem Collaborated extensively with software developers and testers on the Hjälpmedelstjänsten 2.0 team, ensuring seamless integration of data and functionality, thereby contributing significantly to the project's success.
      \techItem Frontend in \textbf{React}. Backend with \textbf{Java EE} and \textbf{WildFly/Thorntail}. Database management with \textbf{H2} and \textbf{MySQL}. Infrastructure setup using \textbf{OpenShift} and containerization with \textbf{Docker}. Cloud storage solutions with \textbf{Amazon S2}. Inventory indexing with \textbf{Elasticsearch}. Build and dependency management with \textbf{Maven}. Version control with \textbf{Git}. Running on \textbf{Linux/Unix}. Data processing with \textbf{ETL}. Project management following \textbf{Scrum} methodology.
    \end{rSubsection}

    \begin{rSubsection}{SAAB AB}{February 2017 -- April 2018}{9LV CMS - Software Developer}{Järfälla}
      \bItem Key member of a senior developer team on a naval management subsystem, employing agile methodologies. Contributed significantly to delivering high-quality software solutions. Served as team representative in Scrum of Scrums, managing sprint backlogs and planning, aligning with project objectives for efficient workflow. Oversaw project phases from architecture to documentation, showcasing comprehensive skills and attention to detail.
      \techItem Backend \textbf{Java 8}. Embedded in \textbf{C++ \& Golang}. Automation with \textbf{Python} and \textbf{Bash}. Infrastructure management and orchestration using \textbf{CoreOS \& Docker} on \textbf{Linux}. Database management with \textbf{MongoDB}. Real-time messaging with \textbf{ESB} and \textbf{JMS}. Security and authentication using \textbf{Kerberos} and \textbf{LDAP}. Parser generation with \textbf{ANTLR4}. Version control with \textbf{Git}. Project management and team organization following \textbf{Scrum} methodology.
    \end{rSubsection}

    \begin{rSubsection}{PIERCE AB}{August 2016 -- December 2016}{E-commerce platform - Software Developer}{Stockholm}
      \bItem Enhanced backend systems for e-commerce platforms (24MX, XLMoto, Sledstore), optimizing API performance and product data retrieval with Elasticsearch. Conducted load tests for system optimization and developed an understanding of client relationship importance in consultancy.
      \techItem Backend development using \textbf{Java EE} and \textbf{Play Framework}. Container orchestration with \textbf{Docker} and \textbf{Docker Swarm}. Application server management using \textbf{Payara}. Database solutions with \textbf{Microsoft SQL Server}. Search engine implementation with \textbf{Elasticsearch}. Messaging systems with \textbf{JMS}. Performance testing using \textbf{JMeter}. Version control with \textbf{Git}. Running on \textbf{Linux/Unix}. Agile project management with \textbf{Scrum}.
    \end{rSubsection}

    \begin{rSubsection}{GOVERNMENT AGENCY}{September 2013 -- June 2014}{Client solutions - Software Developer}{Stockholm}
      \bItem Represented Saab AB in a client-facing role, focusing on custom software integration and development for on-site system upgrades. Collaborated closely with client to ensure solutions met specific operational needs, demonstrating technical expertise and a customer-service orientation.
      \techItem Backend development with \textbf{Java EE}. Database solutions with \textbf{PostgreSQL}. Directory services with \textbf{LDAP}. Build and dependency management with \textbf{Maven}. Version control with \textbf{Git}. Operating in a \textbf{Linux} environment.
    \end{rSubsection}
    \pagebreak

    \begin{rSubsection}{SAAB AB}{March 2012 -- August 2016}{Mission data management - Software Developer}{Järfälla}
      \bItem Contributed to software development for electronic warfare libraries in air, land, and sea-based defense systems using agile methodologies, focusing on functionality and reliability. Engaged in full software lifecycle from requirements to delivery and documentation. Later promoted to Technical Design Authority for EWLib, acknowledging expertise and contributions.
      \techItem Backend development with \textbf{Java EE}, \textbf{Eclipse RCP}, and \textbf{Spring}. Application server management using \textbf{JBoss EAP} and \textbf{Wildfly}. Database solutions with \textbf{DB2}, \textbf{PostgreSQL}, and \textbf{H2}. Messaging using \textbf{JMS}. Directory services with \textbf{LDAP}. Build and dependency management with \textbf{Maven}. Version control with \textbf{Git}. Agile project management following \textbf{Scrum} methodology.
    \end{rSubsection}

    \begin{rSubsection}{INNVENTIA AB}{February 2012 -- July 2012}{PPA Carbon Calculator - Software Developer}{Stockholm}
      \bItem Enhanced the PPA Carbon Calculator by adding new functionalities for office and journalism data administration, journalism impact calculation, online content analysis, and end-to-end distribution of prints, expanding the system's capabilities.
      \techItem Backend development with \textbf{Java EE} and web development using \textbf{Vaadin}. Web server management using \textbf{Tomcat}. Database management with \textbf{MySQL}. Build and dependency management with \textbf{Maven}. Version control with \textbf{Git}. Operating in a \textbf{Linux} environment.
    \end{rSubsection}

    \begin{rSubsection}{VETENSKAPSRÅDET}{February 2012}{Digital compilation of annual grant reports - Software Developer}{Stockholm}
      \bItem Developed specialized software to compile digital annual grant reports for Vetenskapsrådet, automating data extraction from their intranet and streamlining report generation.
      \techItem Development in \textbf{Java}. Build and dependency management with \textbf{Maven}. Operating in a \textbf{Linux} environment.
    \end{rSubsection}

    \begin{rSubsection}{INNVENTIA AB}{July 2011 -- November 2011}{PPA Carbon Calculator - Software Developer}{Stockholm}
      \bItem Developed the Professional Publishers Association (PPA) Carbon Calculator by adapting the existing Book Carbon Calculator framework. This demonstrated technical proficiency in customizing research-based frameworks to meet industry-specific requirements.
      \techItem Backend development with \textbf{Java EE} and web applications using \textbf{Vaadin}. Web server management with \textbf{Tomcat}. Database solutions with \textbf{MySQL}. Build and dependency management with \textbf{Maven}. Operating in a \textbf{Linux} environment.
    \end{rSubsection}
  \end{rSection}
  \pagebreak

  \begin{rSection}{Employment history}
  {\bf BYTELOPE AB, Stockholm}
    \hfill {\em April 2021 -- Present } \\
    { Permanent employment, full-time. }

    {\bf SVENSK TRAVSPORT AB, Stockholm}
    \hfill {\em June 2020 -- March 2021 } \\
    { Permanent employment, full-time including on-call. }

    {\bf COMBITECH AB, Stockholm}
    \hfill {\em August 2016 -- June 2020 } \\
    { Permanent employment, full-time. }

    {\bf SAAB AB, Järfälla}
    \hfill {\em November 2012 -- August 2016 } \\
    { Permanent employment, full-time. }

    {\bf INNVENTIA AB, Stockholm}
    \hfill {\em February 2012 -- July 2012 } \\
    { Project employment, part-time. }

    {\bf ACADEMIC WORK AB, Stockholm}
    \hfill {\em January 2012 -- November 2012 } \\
    { Permanent employment, full-time. }

    {\bf INNVENTIA AB, Stockholm}
    \hfill {\em June 2011 -- July 2011 } \\
    { Project employment, part-time. }

  \end{rSection}

  \begin{rSection}{Education}
  {\bf KTH Royal Institute of Technology}
    \hfill {\em 2007--2011 } \\
    { B.Sc. in Information \& Communication Technology (177 credits completed, incomplete) } \\
    { Thesis "BookCarbon: A System for Tracking Carbon Dioxide Emissions in the Life Cycle of a Book". }

    {\bf Cambridge English: Proficiency (CPE) - Grade B}
    \hfill {\em 2006 } \\
    { Certificate awarded by Cambridge Assessment English. }

    {\bf International IT College of Sweden}
    \hfill {\em 2004--2007 } \\
    { Upper Secondary School Diploma: Natural Science Program. } \\
    { Specialization in Mathematics \& Computer Science. }
  \end{rSection}

  \begin{rSection}{Courses}
  {\bf INFORMATOR AB}
    \hfill {\em 2019 (2-day course) } \\
    { Agile Architecture Fundamentals [T1101]. }

    {\bf COMBITECH GROW}
    \hfill {\em 2019 (2-day course) } \\
    { Software Craftsmanship. }

    {\bf INFORMATOR AB}
    \hfill {\em 2017 (2-day course) } \\
    { Effective Coding Principles and Patterns in Java 8 [T1627]. }

    {\bf ECLIPSESOURCE GMBH}
    \hfill {\em 2014 (3-day course) } \\
    { Advanced Eclipse RCP. }

    {\bf LEAST TECHNICAL/TACTICAL CONSULTING AND TRAINING}
    \hfill {\em 2013 (2-day course)} \\
    { Evolution of Air Power – Tactics and connections to Technology. }
  \end{rSection}

\end{document}
